The importance of transient resonances in extreme-mass-ratio inspirals

### 2016-11-21 res_char.tex
Jon's suggestions

\begin{figure}
\centering
%\includegraphics[width=0.46\textwidth]{Fig_overlap_vs_time}
\includegraphics[width=0.4\textwidth]{Fig_overlap}
\caption{\label{fig:overlap-dephasing}The overlap computed between the full evolution and an adiabatic evolution for an illustrative EMRI system with $p=7.85$, as a function of time, including only the parts of the waveforms within some $\Delta t$ of $t$, arbitrarily chosen to give $25$ independent (non-overlapping) calculations. The time $t = t\sub{res}$ is when the full evolution crosses the $2$:$3$ resonance.}
\end{figure}

@@

To evolve the orbits, we start with orbital periods of $T_0$ and then use the analytic kludge (AK) prescription of Barack and Cutler~\cite{Barack2004}. This is similar to the NK approach, but uses a series of Keplerian ellipses rather than Kerr geodesics. Evolution of the orbit includes the effects of periapse precession, Lense--Thirring
precession, and radiation reaction calculated using PN expressions.\footnote{While the AK approach does include these relativistic effects, it does not capture the full nature of the evolution: for example, it assumes that the angle between the orbital angular momentum and the SMBH spin is constant~\cite{Barack2004}, whereas radiation reaction should push the orbital plane towards being anitaligned~\cite{Flanagan2007}. The approximate nature of the AK evolution should not effect our results more than the uncertainty in the initial conditions for EMRI orbits.} AK waveforms are less computationally expensive than NK waveforms, allowing us to simulate a large population of EMRIs. We follow inspirals until the last stable orbit (LSO).\footnote{The LSO is determined numerically by calculating the roots of $V_r(r) = 0$, which we denote in ascending order by $r_4 \leq r_3 \leq r\sub{p} \leq r\sub{a}$, and stopping the evolution when $r_3 = r_p$, which designates the orbit as marginally stable. This ignores the (small) influence of the self-force~\cite{Isoyama2014}.} Each of these systems is then evolved backwards for some time $t\sub{insp}$, chosen uniformly from the range $[0,t\sub{life}]$ for a mission lifetime $t\sub{life}$, and the expected GWs are calculated using the AK formalism.

>>>>

\begin{figure}
\centering
%\includegraphics[width=0.46\textwidth]{Fig_overlap_vs_time}
\includegraphics[width=0.4\textwidth]{Fig_overlap}
\caption{\label{fig:overlap-dephasing}The overlap computed between the full evolution and an adiabatic evolution for an illustrative EMRI system with $p=7.85$, as a function of time, including only the parts of the waveforms within some $\Delta t$ of $t$, arbitrarily chosen to give $25$ independent (non-overlapping) calculations. The time $t = t\sub{res}$ is when the full evolution crosses the $2$:$3$ resonance ($p \simeq 7.67$, $e \simeq 0.674$, $\cos(\iota) \simeq 0.497$).}
\end{figure}

@@

To evolve the orbits, we start with orbital periods of $T_0$ and then use the analytic kludge (AK) prescription of Barack and Cutler~\cite{Barack2004}. This is similar to the NK approach, but uses a series of Keplerian ellipses rather than Kerr geodesics. Evolution of the orbit includes the effects of periapse precession, Lense--Thirring
precession, and radiation reaction calculated using PN expressions.\footnote{While the AK approach does include these relativistic effects, it does not capture the full nature of the evolution: for example, it assumes that the angle between the orbital angular momentum and the SMBH spin is constant~\cite{Barack2004}, whereas radiation reaction should push the orbital plane towards being anitaligned~\cite{Flanagan2007}. The approximate nature of the AK evolution should not effect our results more than the uncertainty in the initial conditions for EMRI orbits (for example, how loss-cone dynamics are modified by the SMBH's spin~\cite{Amaro-Seoane2012b}).} AK waveforms are less computationally expensive than NK waveforms, allowing us to simulate a large population of EMRIs. We follow inspirals until the last stable orbit (LSO).\footnote{The LSO is determined numerically by calculating the roots of $V_r(r) = 0$, which we denote in ascending order by $r_4 \leq r_3 \leq r\sub{p} \leq r\sub{a}$, and stopping the evolution when $r_3 = r_p$, which designates the orbit as marginally stable. This ignores the (small) influence of the self-force~\cite{Isoyama2014}.} Each of these systems is then evolved backwards for some time $t\sub{insp}$, chosen uniformly from the range $[0,t\sub{life}]$ for a mission lifetime $t\sub{life}$, and the expected GWs are calculated using the AK formalism.
